\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage[english]{babel}
 
\title{02.507 Academic Writing Homework 9 Solution}
%\setlength{\parindent}{4em}
%\setlength{\parskip}{1em}
%\renewcommand{\baselinestretch}{1.0}
\author{Chang Liu ~\\ chang\_liu@student.uml.edu} 

\begin{document}

\maketitle

\section{P54 (b)}

(ii) After the second world war, more \underline{focus} has been given on the \underline{style} of the car maker's products to encourage more frequent model changes.

(iii) From the 1970s the industry is \underline{criticized} because most vehicles are \underline{inefficient}, as they are in a \underline{waste} of petrol.


\section{P54 (c)}

(ii) Today some of the most famous brands in the world is owned by the industry.

(iii) However, the increased competition and saturated markets currently post threat to many car makers.

\section{P61 (5) Practice C}

Toto's best-selling Washlet lavatory is used in most Japanese homes as they provide valued privacy in many small and crowded flats, However, in Europe and America, they face a variety of difficulties due to their own rules of lavatory design and electrical socket for installation.


\section{P144 (5) Practice C}

(b) Math is the most popular future course among all the courses for these students.

(c) The average age of these student is 21 years old

(d) Most of the students are 23 years old, and the second frequent age is 22 years old.

(e) Swimming is more popular than other sports, but the difference between all these favourite sports is not very significant.

(f) Psychology and architecture are the least popular future courses they want to take.



\end{document}