\documentclass{article}
\usepackage{}

\author{Chang Liu}
\title{Example sentense}
\begin{document}

\maketitle


\section{Example}
Faculty across the College agree that mastery of the skills of written argument, including critical thinking, problem solving, organization of ideas, and clarity and power of expression, is of enormous importance both in academic work during residence in the College and in the world of work beyond the College. Writing is how we know what it is that we know, because our ability to explain a subject clearly and precisely is an ultimate test of having learned it. Writing enables us to persuade others of the truth, the utility, or the beauty of what we know, and in our writing we can make our ideas have an impact on the world at large.



\section{Analysis}

\subsection{Point1}
In traditional way, we will use the \textbf{How to do something....}, but here, using \textbf{mastery of the skills ...} shows better way of expressing the same meaning.

\subsection{Point2}
Similarly, using \textbf{It is very important that ...} is also very common, but in our papers, using \textbf{It is of enormous importance} instead can give us more efficient meaning.

\subsection{Point3}
\textbf{Writing enables us to persuade others of what we have learned} is also better than what we thought, usually we will use \textbf{ Writing helps us ...}, here using \textbf{enables} can be a good start.

\subsection{Point4}
In another way, \textbf{because our ability to explain a subject clearly and precisely is an ultimate test of having learned it}, is also better than we what say that \textbf{It shows that how well we learned is an ultimate test...}


\section{Conclusion}

In short, this concise paragraph gives us a very good idea of how we can use \textbf{long sentence} to say something precisely and accurately. And in the lecture, I also learned that usually what we write is too casual, we may use another way in our daily writing and improve it more.

And using long and short sentence at the same time, can make the reader more attracted by your paper and generate a better result. So just take a look of good writing papers and practise more about it.

\end{document}
